workshop

### 2022-09-19 scripts/workshop/workshop.Rmd
add nmds

>>>>

NMDS with bray-curtis
```{r}
set.seed(8878896)
nmds <- metaMDS(abundance_mat, distance = "bray")

plot(nmds)

nmds_scores <- as_tibble(scores(nmds))
nmds_scores$siteID <- community_mat$siteID

nmds_scores_summ <- left_join(comm_summ, nmds_scores, by = "siteID")
nmds_scores_summ$Month <- factor(nmds_scores_summ$Month, levels = c("Feb", "Mar", "Apr", "May", "Jun", "Jul"))
nmds_scores_summ %<>% mutate(pc1Rank=dense_rank(NMDS1))

nmds_scores_summ %>% ggplot(.,aes(x=NMDS1, y = cc)) + geom_point() + geom_smooth(method = "loess")
```
